How has the Amazon been construed as a problem? Preliminary Analysis

### 2022-04-06 Draft_April_2022/Full_draft_20220401.rmd
#newstuff
predicted figure 1; updated rmd and qmd

---
title: How has the Brazilian Amazon been constructed as a problem? An analysis of
  presidential speeches since 1985
author:
- Livio Silva-Muller^[Phd Candidate, The Geneva Graduate Institute , livio.silva@graduateinstitute.ch]
- Henrique Sposito^[Phd Candidate, The Geneva Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
date: "April 2022"
output:
  word_document:
    reference_docx: template.docx
  pdf_document: default
  html_document:
    df_print: paged
bibliography: references.bib
csl: chicago.csl
abstract: This paper ...
---

@@

In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses. Building on @hirschman1963 concept of chosen problems in policy making, we propose a framework to identify how problem-construction varies over time, by location, and between and within governments. Although problem-construction takes place in a series of instances (e.g. policy committees, legislative bodies, media, etc.), we analyze the case of political discourse by Brazilian presidents since 1985. We opt for presidential speeches for three reasons. First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004]. In turn, policy perception is key for policy adoption and implementation [@alesina2009]. The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations [@assunção2015; @capobianco2019; @capobianco2021]. Thus, understanding how policy comes about discursively is important. Second, environmental discourse at the top can help expand or restrict what types of behaviors are accepted in the ground. When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally, but also incites responses, shapes expectations, and feeds into the behavior of many actors involved with the Amazon, from investors to agribusiness to local farmer[@brice2021; @harris2021; @miranda2021]. This is especially pertinent for deforestation as previous research found that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground [@capobianco2019; @campbell2015]. Unpacking discourse at the top might help us raise hypotheses about environmental outcomes that are culturally situated. Finally, as our theoretical framework suggests, problem-construction varies by geographic location. Presidential discourses take place in a series of sites with diverse audiences: from launching a new bridge in a small municipality in the middle of the Amazon, to a keynote speech in a business association in São Paulo, to the UN general assembly in New York city. Working with presidential discourses allows us to identify this variation in meaningful ways and better how the Amazon is socially constructed.

@@

Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year. The smoothed curved controls incidence deforestation rates, economic situation, and election year (see appendix for methodological details). We observe various local maxima: 1989, 1992, 2004, 2009, 2015, and 2019. These points coincide exogenous events that helps us explain the rises and falls of the Amazon in presidential discourse.

>>>>

---
title: How has the Brazilian Amazon been constructed as a problem? An analysis of
  presidential speeches since 1985
author:
- Livio Silva-Muller^[Phd Candidate, The Geneva Graduate Institute , livio.silva@graduateinstitute.ch]
- Henrique Sposito^[Phd Candidate, The Geneva Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
date: "April 2022"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document:
    reference_docx: template.docx
bibliography: references.bib
csl: chicago.csl
abstract: This paper ...
---

@@

In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses. Building on @hirschman1963 concept of chosen problems in policy making, we propose a framework to identify how problem-construction varies over time, by location, and between and within governments. Although problem-construction takes place in a series of instances (e.g. policy committees, legislative bodies, media, etc.), we analyze the case of political discourse by Brazilian presidents since 1985. We opt for presidential speeches for three reasons. First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004]. In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lópez2020]. The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations [@assunção2015; @capobianco2019; @capobianco2021]. Thus, understanding how policy comes about discursively is important. Second, environmental discourse at the top can help expand or restrict what types of behaviors are accepted in the ground. When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally, but also incites responses, shapes expectations, and feeds into the behavior of many actors involved with the Amazon, from investors to agribusiness to local farmer[@brice2021; @harris2021; @miranda2021]. This is especially pertinent for deforestation as previous research found that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground [@capobianco2019; @campbell2015]. Unpacking discourse at the top might help us raise hypotheses about environmental outcomes that are culturally situated. Finally, as our theoretical framework suggests, problem-construction varies by geographic location. Presidential discourses take place in a series of sites with diverse audiences: from launching a new bridge in a small municipality in the middle of the Amazon, to a keynote speech in a business association in São Paulo, to the UN general assembly in New York city. Working with presidential discourses allows us to identify this variation in meaningful ways and better how the Amazon is socially constructed.

@@

Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year. The smoothed curved controls incidence for deforestation rates, economic situation, speaker, and election year (see appendix for methodological details). We observe various local maxima: 1989, 1992, 2004, 2009, 2015, and 2019. These points coincide exogenous events that helps us explain the rises and falls of the Amazon in presidential discourse.

### 2022-04-06 analysis/analysis_livio.Rmd
#newstuff
predicted figure 1; updated rmd and qmd

@@

@@

>>>>

amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")

AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds")

amazon_def_year <- amazon_def_year %>% rename(def_year = "area km\u00b2")

amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>%
  rename(def_year = "area km\u00b2")

@@

pop %>% count(amazon_speech, year) %>%
  group_by(year) %>%
  left_join(perc1) %>%
  left_join(amazon_def_year)%>%
  filter(amazon_speech==1) %>%
  ggplot(., aes(x = year, y = perc)) +
  geom_smooth(color="black", size=.75, se=FALSE, method="loess")+
  geom_line(color="darkolivegreen")+
  scale_y_continuous(labels = percent_format())+
  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
  labs(
    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
    subtitle = "Sample composed by 6130 presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "right"
  )

```{r Amazonian speeches by year II, echo=FALSE, message=FALSE, warning=TRUE, echo=FALSE, paged.print=TRUE}

@@

```{r Amazonian speeches by year III, echo=FALSE, message=FALSE, warning=TRUE, echo=FALSE, paged.print=TRUE}

pop2 <- pop %>% count(amazon_speech, year, president) %>%
  group_by(year, president) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1) %>%
  mutate(election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))

  pop2 <- left_join(pop2, AAI, by = "year")
  pop2 <- left_join(pop2, amazon_def_year, by = "year")

model <- lm(perc ~ AAI+ def_year + president + election_year, data=pop2)

pop2$predicted = predict(model, pop2)

pop2 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(size=.65, aes(x=year, y=perc, color="real share"), linetype= "solid")+
  geom_line(size=.5, aes(x=year, y=predicted, color="Predicted share"), linetype="dotted")+
  scale_color_manual(values=c("real share"="darkolivegreen", "Predicted share"= "black"))+
  scale_y_continuous(labels = percent_format())+
  labs(
    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
    subtitle = "Sample composed by 6130 presidential speeches since 1985",
    caption = "Predicted share curve controls for yearly deforestation rates, yearly inflation, and president", color='Y series') +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "bottom"
  )
